### 2020-05-19 writeup/transfer.tex
wip

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{figures/model_shift_phase_transition.eps}
	\caption{Positive vs negative transfer as a parameter of the task model distances.}
	\label{fig_model_shift_phasetrans}
\end{figure}

>>>>

\begin{figure}
	\begin{subfigure}[b]{0.31\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
		\caption{Task model similarity}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.31\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
		\caption{Source task noise level}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.31\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
		\caption{\# Source task datapoints}
	\end{subfigure}
	\caption{Comparing the test error of multi-task learning to single-task learning: we observe transitions from positive to negative transfer as a parameter of: (a) Task model similarities (Proposition \ref{prop_dist_transition}); (b) Source task noise level (Proposition \ref{prop_var_transition}); (c) Source task datapoints (Proposition \ref{prop_data_size}).}
	\label{fig_model_shift_phasetrans}
\end{figure}
